---
title: "vignette for binomial"
author: "Colin Donovan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

##Using the Binomial Package
***
#####The binomial package is a fairly simple and straightforward package, directed at those trying to compute, summarize, and/or visualize simple binomial distribution-related calculations.

####Possible Computation

There are 5 *basic* computational functions included in the binomial package:

* bin_mean, which calculates mean
* bin_mode, which calculates mode
* bin_variance, which calculates variance
* bin_kurtosis, which calculates kurtosis
* bin_skewness, which calculates skewness

*Note: all the functions listed above take inputs 'trials' and 'prob'.*

...and here's an example of how you might use them:

```{r bin_mean example}
#bin_mean(10, 0.3)
#where 10 is the number of trials, and 0.3 is the probability of something occuring
bin_mean(10, 0.3)
#gives the mean, or average
```

```{r bin_mode example}
#bin_mode(10, 0.3)
#where 10 is the number of trials, and 0.3 is the 
bin_mode(10, 0.3)
#gives the mode
#depending on your input, this can return either 1 integer, or 2 integers
```
for more information on this, visit:

[mode information](https://en.wikipedia.org/wiki/Binomial_distribution#Mode)

```{r bin_variance example}
#bin_variance(10, 0.3)
#where 10 is the number of trials, and 0.3 is the probability of something occuring
bin_variance(10, 0.3)
#gives the variance of the probability distribution
```

```{r bin_kurtosis example}
#bin_kurtosis(10, 0.3)
#where 10 is the number of trials, and 0.3 is the probability of something occuring
bin_kurtosis(10, 0.3)
#gives the kurtosis of the probability distribution
```

```{r bin_skewness example}
#bin_skewness(10, 0.3)
#where 10 is the number of trials, and 0.3 is the probability of something occuring
bin_skewness(10, 0.3)
#gives the skewness of the probability distribution
```

On top of these, there are 4 *main* computational functions included in the binomial package:

* bin_choose, which calculates the binomial coefficient
  (see [Binomial Coefficient](https://en.wikipedia.org/wiki/Binomial_coefficient) for more information)
* bin_probability, which calculates the probability of a given event occuring over a certain number of trials
* bin_distribution, which calculates probability distribution, and displays it in data frame form
* bin_cumulative, which calculates cumulative probability distrution, and displays it in data frame form

*Note: the functions listed above take some combination of inputs 'trials', 'success' and 'prob'.*
*except bin_choose, which takes n and k.*

...and here's an example of how you might use them:

```{r bin_choose example}
#bin_choose(5, 2)
#which can be read, 5 choose 2
#this is like having 5 objects, and seeing how many different ways you can pick 2 objects from that assortment
bin_choose(5, 2)
#gives the number of combinations possible
```

```{r bin_probability example}
#bin_probability(5, 10, 0.5)
#this is the only function with 3 arguments, success, trials, and prob
bin_probability(5, 10, 0.5)
#which returns a the probability of a specified number of successes occuring over 
```

```{r bin_istribution example}
#bin_distribution(10, 0.5)
#this should give you the probability distribution in data frame form
bin_distribution(10, 0.5)
#this has class 'bindis', which will allow you to plot later
```

```{r bin_cumulative example}
#bin_cumulative
#this should return a data frame of the probability distribution, as well as the cumulative probability distribution
bin_cumulative(10, 0.5)
#this has class 'bincum' which will allow you to plot later
```
***

####Possible Summarization

There is 1 *main* summarizing function included in the binomial package:

* bin_variable


...and here's how to call and use it:
```{r}
#bin_variable(10, 0.3)
#there are three summarization options:
object3 <- bin_variable(10, 0.3)
object3
#which gives a VERY basic summary
print(object3)
#another way to call it
summary(object3)
#which gives a more comprehensive summary of the binomial variable
```


***
####Possible Visualizations

There are 2 *main* computational functions that can be easily visualized:

Using the plot() function:

* bin_cumulative
* bin_distribution

...cumulative probabilities and probability distribution can be plotted.

Any object of class bindis or bincum can be plotted. In other words, this means that if you assign a name to a data frame created by either bin_cumulative or bin_distribution, it should be 'plottable' by the base function plot().

Here are some examples:

```{r}
#first assign your bin_distribution an object name
object1 <- bin_distribution(10, 0.3)
#then simply run it through the plot() function
plot(object1)
```

```{r}
#same thing with bin_cumulative
#first assign your bin_cumulative an object name
object2 <- bin_cumulative(10, 0.3)
#then just run it through the plot() function
plot(object2)
```
***